Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
Add microtype package.
spelling

% setup
\documentclass[10pt]{article}
\usepackage{color}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{multicol}

@@

The intent of an election is to determine the true will of the voters.
If there is any possibility for a third party to discover the content of
an individual's ballot, then the voter's own will may be undermined by coercion.
Therefore a voting system must maintain secrecy of invididuals' votes to avoid
the possibility that a voter may receive retribution or reward for casting a vote
in any particular way.

@@

At the heart of Helios is a single ElGamal keypair. The secret key is known only to the Helios
server, but the public key can be accessed in some way by all participants.

@@

In both Scantegrity and Helios, the most fundamental secret is a key. In Scantegrity, this is the
seed to the pseudorandom number generator used to create Table P; and in Helios, it is a single
ElGamal keypair used for all encryption/decryption operations during a particular election.

@@

Public-key encryption could potentially solve some of these issues; however, it is not feasible
today to require each voter to maintain his/her own keypair.

>>>>

% setup
\documentclass[10pt]{article}
\usepackage{color}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{microtype}

@@

The intent of an election is to determine the true will of the voters.
If there is any possibility for a third party to discover the content of
an individual's ballot, then the voter's own will may be undermined by coercion.
Therefore a voting system must maintain secrecy of individuals' votes to avoid
the possibility that a voter may receive retribution or reward for casting a vote
in any particular way.

@@

At the heart of Helios is a single ElGamal key pair. The secret key is known only to the Helios
server, but the public key can be accessed in some way by all participants.

@@

In both Scantegrity and Helios, the most fundamental secret is a key. In Scantegrity, this is the
seed to the pseudorandom number generator used to create Table P; and in Helios, it is a single
ElGamal key pair used for all encryption/decryption operations during a particular election.

@@

Public-key encryption could potentially solve some of these issues; however, it is not feasible
today to require each voter to maintain his/her own key pair.
